Online Laterality Battery Pre-Processing - short version

### 2020-02-03 battery-preprocessing_v3_DB.Rmd
renamed Trial.Number as Trial and included this when reading RDT. In principle might want to look at how LI changes over blocks, but would need also to code block. Trial refers to trial within block - is there a block code in Gorilla? If not we could compute this. Could check Carey idea that *initial* performance is most informative - seems unlikely but could check!

  if (d ==2){
    data_file <-  "./dat2/day2_combined.csv"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1,display=="e_Task") # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}
#check that colnames are the same
colcomp<-data.frame(colnames(all_dat1)[order(colnames(all_dat1))])
colnames(colcomp)[1]<-'name1'
ncol2 <-length(colnames(all_dat2))
colcomp$name2<-NA
colcomp$name2[1:ncol2]<-colnames(all_dat2)[order(colnames(all_dat2))]

@@

```{r RToutlierfunction}
remove.outliers <- function(origdat,lowcut,zcut){
# Outlier removal put in separate function, as needed to reuse when considering t-test
# Hoaglin, D. C., & Iglewicz, B. (1987). Fine-tuning some resistant rules for outlier labelling. Journal of the American Statistical Association, 82(400), 1147-1149.

# origdat is the dataframe with data for outlier removal, mycolname is name of variable 
# for outlier removal (usually RT), lowcut is a cutoff value below which data excluded
# (typically v fast responses that are implausible, e.g. 201 ms for RT)
# and zcut is the constant in Hoaglin-Iglewicz method (usually 2.2)

@@

```{r read_face_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_dat1
  if (d==2)
  {origfile <- all_dat2}
#As with earlier reading in, we default to saving CF_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Chimeric faces (Karlsson, Johnstone, & Carey, 2019)"
wanted <- c("subject", "stimuli", "Response", "RT", "l_hemiface", "r_hemiface") # select wanted columns
CF_dat2 <- procdata(origfile,wanted,task)

@@

CF_same2 <- CF_dat2[CF_dat2$l_hemiface == CF_dat2$r_hemiface,] # create data frame for non-chimeras
CF_dat2 <- CF_dat2[CF_dat2$l_hemiface != CF_dat2$r_hemiface,] # remove items where same expression in both hemifaces
CF_dat2 <- remove.outliers(CF_dat2,200,2.2)
outliertable<-table(CF_dat2$subject,CF_dat2$outlier)
print(outliertable)
if (d==1)
{CF_dat1 <- CF_dat2
 CF_same1 <- CF_same2}
}
```

@@

# new data
wanted <- c("subject", "Correct", "RT", "ANSWER","Response") # select wanted columns
RDT_dat2 <- procdata(origfile,wanted,task) #Here we reuse the procdata function that we developed for processing Chimeric faces data - just does some generic processing

@@

cor1 <- cor(demographics$Day1_finger.easy_LI,demographics$Day2_finger.easy_LI,use='complete.obs')
plot(demographics$Day1_finger.easy_LI,demographics$Day2_finger.easy_LI,main='Finger easy LI')
abline(v=0)
abline(h=0)
text(40,10,paste0('r = ',round(cor1,3)))
cor2 <- cor(demographics$Day1_finger.hard_LI,demographics$Day2_finger.hard_LI,use='complete.obs')
plot(demographics$Day1_finger.hard_LI,demographics$Day2_finger.hard_LI,main='Finger hard LI')
abline(v=0)
abline(h=0)
text(40,10,paste0('r = ',round(cor2,3)))

@@

- Burt, D. M., & Perrett, D. I. (1997). Perceptual asymmetries in judgements of facial attractiveness, age, gender, speech and expression. Neuropsychologia, 35(5), 685–693.
- Innes, B. R., Burt, D. M., Birch, Y. K., & Hausmann, M. (2016). A leftward bias however you look at it: Revisiting the emotional chimeric face task as a tool for measuring emotion lateralization. Laterality: Asymmetries of Body, Brain and Cognition, 21(4-6), 643–661.
- Karlsson, E. M., Johnstone, L. T., & Carey, D. P. (2019). The depth and breadth of multiple perceptual asymmetries in right handers and non-right handers. Laterality: Asymmetries of Body, Brain and Cognition, 24(6), 707-739.

>>>>

  if (d ==2){
    data_file <-  "./dat2/day2_combined.csv"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1,display=="e_Task") # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}
#check that colnames are the same
colcomp<-data.frame(colnames(all_dat1)[order(colnames(all_dat1))])
colnames(colcomp)[1]<-'name1'
ncol2 <-length(colnames(all_dat2))
colcomp$name2<-NA
colcomp$name2[1:ncol2]<-colnames(all_dat2)[order(colnames(all_dat2))]

@@

```{r RToutlierfunction}
remove.outliers <- function(origdat,lowcut,zcut){
# Outlier removal put in separate function, which can be applied to different task RTs.
# 
# origdat is the dataframe with data for outlier removal, mycolname is name of variable 
# for outlier removal (usually RT), lowcut is a cutoff value below which data excluded
# (typically v fast responses that are implausible, e.g. 201 ms for RT)
# and zcut is the constant in Hoaglin-Iglewicz method (usually 2.2)

@@

```{r read_face_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_dat1
  if (d==2)
  {origfile <- all_dat2}
#As with earlier reading in, we default to saving CF_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Chimeric faces (Karlsson, Johnstone, & Carey, 2019)"
wanted <- c("subject", "stimuli", "Response", "RT", "l_hemiface", "r_hemiface") # select wanted columns
CF_dat2 <- procdata(origfile,wanted,task) #use generic function (see above) to read in relevant columns

@@

CF_same2 <- CF_dat2[CF_dat2$l_hemiface == CF_dat2$r_hemiface,] # create data frame for non-chimeras
CF_dat2 <- CF_dat2[CF_dat2$l_hemiface != CF_dat2$r_hemiface,] # remove items where same expression in both hemifaces
CF_dat2 <- remove.outliers(CF_dat2,200,2.2) #use generic outlier removal function
outliertable<-table(CF_dat2$subject,CF_dat2$outlier)
print(outliertable)
if (d==1)
{CF_dat1 <- CF_dat2
 CF_same1 <- CF_same2}
}
```

@@

# new data
wanted <- c("Trial","subject", "Correct", "RT", "ANSWER","Response") # select wanted columns
RDT_dat2 <- procdata(origfile,wanted,task) #Here we reuse the procdata function that we developed for processing Chimeric faces data - just does some generic processing

@@

cor1 <- cor(demographics$Day1_finger.easy_LI,demographics$Day2_finger.easy_LI,use='complete.obs')
plot(demographics$Day1_finger.easy_LI,demographics$Day2_finger.easy_LI,main='Finger easy LI')
abline(v=0)
abline(h=0)
text(-5,20,paste0('r = ',round(cor1,3)))
cor2 <- cor(demographics$Day1_finger.hard_LI,demographics$Day2_finger.hard_LI,use='complete.obs')
plot(demographics$Day1_finger.hard_LI,demographics$Day2_finger.hard_LI,main='Finger hard LI')
abline(v=0)
abline(h=0)
text(-5,20,paste0('r = ',round(cor2,3)))

@@

- Burt, D. M., & Perrett, D. I. (1997). Perceptual asymmetries in judgements of facial attractiveness, age, gender, speech and expression. Neuropsychologia, 35(5), 685–693.
- Hoaglin, D. C., & Iglewicz, B. (1987). Fine-tuning some resistant rules for outlier labelling. Journal of the American Statistical Association, 82(400), 1147-1149. 
- Innes, B. R., Burt, D. M., Birch, Y. K., & Hausmann, M. (2016). A leftward bias however you look at it: Revisiting the emotional chimeric face task as a tool for measuring emotion lateralization. Laterality: Asymmetries of Body, Brain and Cognition, 21(4-6), 643–661.
- Karlsson, E. M., Johnstone, L. T., & Carey, D. P. (2019). The depth and breadth of multiple perceptual asymmetries in right handers and non-right handers. Laterality: Asymmetries of Body, Brain and Cognition, 24(6), 707-739.
